Manuscript_Github_Pchabaudi_calculateTPM

### 2021-09-01 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_calculateTPM.Rmd
Changing the tpm_fun to be more strict with inputs

chabaudi_transcript_lengths <- select(chabaudi_gene_info, c(Gene.ID, Transcript.Length)) %>% 
  arrange(Gene.ID)

@@

twentyfour_ct_comb <- tpm(chab_count_table, 
                          lengths = chabaudi_transcript_lengths)
```

@@

twentyfour_avgtpm <- list(
  'rMT' = list(
    tpm = twentyfour_rMT_avg,
    experiment = 'rMT'
)

write_csv(twentyfour_rMT,
          file = 'Pchabaudi_TPM_allBioReps.csv')
write_csv(twentyfour_rMT_avg,
          file = 'Pchabaudi_TPM_average.csv')

>>>>

chabaudi_transcript_lengths <- select(chabaudi_gene_info, c(Gene.ID, Transcript.Length)) %>% 
  arrange(Gene.ID) %>% 
  mutate(Geneid = Gene.ID) %>% 
  select(Geneid, Transcript.Length)

@@

twentyfour_ct_comb <- tpm(count_data = chab_count_table, 
                          lengths = chabaudi_transcript_lengths)
```

@@

twentyfour_avgtpm <- list(
  'rMT' = list(
    tpm = twentyfour_rMT_avg,
    experiment = 'rMT'
  )
)

# write_csv(twentyfour_rMT,
#           file = 'Pchabaudi_TPM_allBioReps.csv')

#The current file is slightly different to the new one I wrote, this worries me a lot.

write_csv(twentyfour_rMT_avg,
          file = 'Pchabaudi_TPM_average.csv')
```
